---
title: "Assessment 1 Part 2"
author: "Hnin"
date: '2022-05-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

**R Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents.**

```{r fastfood}
fastfood<-read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```

```{r filtering the data}
#Display the first 10 rows of the data set
knitr::kable(head(fastfood,10)[,1:5])
```

#Assessment 1 Part 2
```{r A copy of csv file}

library(tidyverse)
write.csv(fastfood, "fastfood.csv")
fastfood_data<-read_csv("fastfood.csv")

```

installed.packages("magrittr")

```{r}
fastfood%>%filter(calories>1000)
```
library(tidyverse)


```{r}
#save
dont_eat_this <-fastfood %>% filter(total_fat> 40 & total_carb> 80)
#display
fastfood %>% filter(total_fat> 40 & total_carb> 80) %>% kable()
```

```{r}
library(skimr)
skim(fastfood)
#Summarize a whole dataset
```
#the count of observations for each restaurant.

```{r}
fastfood %>%
  count(restaurant, wt = NULL, sort = TRUE, name = "res_num") %>% 
  kable()
```


#Using `group_by()`to display the summary of the average number of calories for each restaurant.

```{r}
fastfood%>%
  group_by(restaurant)%>%
  summarise(average_cal = mean(calories, trim = 0, na.rm = FALSE)) %>% 
  ungroup() %>% 
  kable()
```
#The following calculates the average calories per type of restaurant which is `average_calories`.

```{r}
average_calories <-
  fastfood %>% 
  group_by(restaurant)%>%
  mutate(average_calories = mean(calories)) %>% 
  ungroup()
head(average_calories %>% select(restaurant,calories,average_calories))
```
#The following calculates the maximum total fat per type of restaurant which is `max_total_fat`.

```{r}
max_total_fat <- fastfood %>% 
  group_by(restaurant) %>%
  mutate(max_total_fat = max(total_fat)) %>% 
  ungroup()
head(max_total_fat %>% select(restaurant,item,total_fat,max_total_fat))
  
```
#The following calculates the minimum cholesterol per type of restaurant which is `min_cholesterol`.

```{r}
min_cholesterol <- fastfood %>% 
  group_by(restaurant) %>%
  mutate(min_cholesterol = min(cholesterol)) %>% 
  ungroup()
head(min_cholesterol %>% select(restaurant,item,cholesterol,min_cholesterol))
  
```

#We can see two types of variables here which are restaurant and total_fat. According to the cheat sheet of ggplot2, we need to identify which the variables belong to discrete, continuous, both discrete or both continuous. 
#As the restaurant belongs to `discrete` and total_fat belongs to `continuous`, the bar chart will be easier to display the the differences of total_fat between the restaurant.
```{r}
# variable_x = restaurant (this is discrete) and variable_y = total_fat (this is continuous)
fastfood %>% 
  group_by(restaurant) %>% 
  ungroup() %>% 
  ggplot(aes(x = restaurant, y = total_fat)) +
  geom_col() +
  labs(x="Names of Restaurant", y="Total Fat", title="Data Visualisation 1", caption = "Image 1:Bar Graph")
```


#The following represents the observations for Mcdonalds to plot sugar variable against protein with `geom_point()`.

```{r}
fastfood %>% 
  select(restaurant, sugar, protein) %>% 
  filter(restaurant=="Mcdonalds") %>% 
  ggplot(aes(sugar,protein)) +
  geom_point(colour = "blue") +
  labs(x="Sugar", y="Protein", title = "Data Visualisation - Mcdonalds", caption = "Image 2:Point Graph")
```
```{r load-packages, include=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
```
